%! TeX root: ../main.tex
\documentclass[../main.tex]{subfiles}

\begin{document}
\section{Topological Rings}
To deal with the topological rings showing up, the notion of admissible rings
will be convenient (taken from \cite[Tag 07E8]{stacks-project}).
\begin{defi}\label{def:admring}
  Let $A$ be a topological ring. We say that $A$ is admissible if
  \begin{itemize}
    \item The element $0 \in A$ has a fundamental system of neighbourhoods
      consisting of ideals.
    \item There exists an ideal of definition, that is, an open ideal $I
      \subset A$ such that every open neighbourhood of $0$ contains $I^n$ for
      some $n$.
    \item It is complete, that is, the natural map
      \begin{equation*}
        A \to \lim_{J \subset A \text{ open ideal}} A/J
      \end{equation*}
      is an isomorphism.
  \end{itemize}
  We say that $A$ is adic if it admits an ideal of definition $I$ such that 
  $I^n$ is open for all $n$.
  Given a topological ring $A$, we denote the category of admissible 
  and adic $A$-algebras (algebras $S$ with continuous morphism $A \to S$) by
  $\Adm A$ and $\Adic A$, respectively.
\end{defi}

\blue{The following results might be not interesting enough to make it into the final
draft}

\begin{lem} \label{lem:iodimage}
  Let $\phi: R \to S$ be a morphism of admissible rings, and let $I \subset R$ be an 
  admissible ideal. Then the ideal $J = \phi(I) \cdot S$ is an ideal of definition in 
  $S$.
\begin{proof}
  Let $U$ be an open ideal of $S$. By continuity of $\phi$, it's preimage
  $U' = \phi^{-1}(U)$ is open in $R$. Hence there is some $n$ with 
  $I^n \subset U'$. But now 
  $$\phi(I)^n = \phi(I^n) \subseteq \phi(\phi^{-1}(U)) \subseteq U$$
  and the claim follows.
\end{proof}
\end{lem}

\begin{lem}\label{lem:infiniteseriesandproducts}
  Let $S$ be an admissible ring, and let $(s_1, s_2, \dots)$ be a sequence with
  elements in $S$. Then $\sum_{i = 1}^\infty s_i$ converges if and only if 
   $\lim_{i \to \infty} s_i = 0$. In this case, the product $\prod_{i=1}^\infty (1 + s_i)$
   exists in $S$.
\begin{proof}
  If the sum converges, $(s_i)_{i \in \N}$ has to be a null-sequence. The
  reverse implication and the convergence of the product follows after writing
  $S \cong \lim_{J} S/J$ for a system of open ideals $J \subset S$. 
\end{proof}

The topology on an admissible ring $R$ with ideal of definition $I$ is coarser
than the $I$-adic topology on $R$
\begin{lem}\label{lem:AdmAdicComp}
  Let $R$ be an admissible ring with ideal of definition $I$. Let $R'$ be the same 
  ring, but equipped with the $I$-adic topology. Then the identity map $R' \to R$
  is continuous. In particular, if a sequence converges with respect to the
  $I$-adic topology, it also converges in $R'$.
\begin{proof}
  It suffices to check that open ideals of $R$ are open in $R'$. 
  Let $J \subset R$ an open ideal. By assumption, there is some $n$ with $I^n
  \subset J$. But now, for any $x \in J$, we have $x + I^n \subset J$. Hence,
  $J$ is open in $R'$.
\end{proof}
\end{lem}

\end{lem}

\end{document}

